Structured Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-10-10 R0V0.tex
Start to review the notation of the sets describing the feedback law
small change on notation

Define also the set of feedback laws
\begin{equation*}
	\Xi=\left\{k^\ast:\mathbb{R}_{\geq0}\times\mathbb{R}^n\to\mathbb{R}^m:k_i^\ast\ \text{has the property}\ \mathscr{K}(i)\right\}.
\end{equation*}

@@

\begin{theorem}\label{thm:main result}
	If there exist a smooth functions $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ such that, for every $(x,\delta x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$, $W=W^\top\succ0$, $W$ is block-diagonal, $Y\in\Xi_Y$ and the pair $(W,Y)$ is a solution to the MI \eqref{eq:MI formulation}, then there exists a solution to Problem~\ref{problem formulation}.
\end{theorem}

@@

Consider a graph $\mathscr{G}=(\mathscr{V},\mathscr{E})$. A \emph{clique} $\mathscr{C}\subset\mathscr{V}$ of the graph $\mathscr{G}$ is the maximal set of nodes that induces a complete subgraph on $\mathscr{G}$. A \emph{clique tree} is a tree that has cliques as its nodes. An algorithm to compute the number of cliques is provided in \cite{BronKerbosch1973}.

>>>>

Define also the set of feedback laws
\begin{align*}
	\Xi=\{k^\ast:\mathbb{R}_{\geq0}\times\mathbb{R}^n\to\mathbb{R}^m:\forall i\in\mathbb{N}_{[1,m]},k_i^\ast\ \text{depends on}\\
	 \text{the components of}\ x\ \text{with indexes given by}\ \mathscr{K}(i)\}.
\end{align*}

@@

\begin{theorem}\label{thm:main result}
	If there exist a smooth functions $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ such that, for every $(x,\delta_x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$, $W=W^\top\succ0$, $W$ is block-diagonal, $Y\in\Xi_Y$ and the pair $(W,Y)$ is a solution to the MI \eqref{eq:MI formulation}, then there exists a solution to Problem~\ref{problem formulation}.
\end{theorem}

@@

Consider a graph $\mathscr{G}=(\mathscr{V},\mathscr{E})$ describing the topology of the network \eqref{eq:general system}. A \emph{clique} $\mathscr{C}\subset\mathscr{V}$ of the graph $\mathscr{G}$ is the maximal set of nodes that induces a complete subgraph on $\mathscr{G}$. A \emph{clique tree} is a tree that has cliques as its nodes. An algorithm to compute the number of cliques is provided in \cite{BronKerbosch1973}.
